---
title: "DV J-Comp"
author: "Vishal N"
date: "2023-03-09"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the csv and storing it in a dataframe df.
```{r}
list.files()
df = read.csv("./datasets/data.csv")
```



Partial df is a subset for a specific state.
```{r}
p_df = subset(df, State.Name=="Andhra Pradesh")
```

Pre processing
```{r}
df=unique(p_df)
head(p_df)
```


```{r}
no_na=complete.cases(p_df)
p_df=p_df[no_na,]
head(p_df)
```

```{r}
col_names=colnames(p_df)
zeroes=col_names[31:95]
```



```{r}
pp_p_df = p_df
for(col in zeroes){
  for(i in seq(1,nrow(pp_p_df),1)){
    if (as.double(pp_p_df[i,col]) == 0.0){
      #print(df[i,col])
      if(i >1 && pp_p_df[i-1,6]==p_df[i,6] ){#  && pp_p_df[i-1,col] != 0&& pp_p_df[i+1,col] != 0){
      avg = (as.double(pp_p_df[i - 1,col]) + as.double(pp_p_df[i+1,col]))/2
      #print(avg)
      pp_p_df[i,col]= avg
      }
    }
  }
}
head(pp_p_df)
```


```{r}
cult_land_based_on_rainfall = lm(NET.CROPPED.AREA..1000.ha. ~ ANNUAL.RAINFALL..Millimeters.,data=pp_p_df)
summary(cult_land_based_on_rainfall)

# plot(cult_land_based_on_rainfall)

plot(pp_p_df$ANNUAL.RAINFALL..Millimeters., pp_p_df$NET.CROPPED.AREA..1000.ha.)
abline(cult_land_based_on_rainfall)
```
👆 Slope is negative so crops suffer in excess rain in AP.



Multiple regresison for predicting Maize production based on MAIZE.AREA..1000.ha. , MAIZE.IRRIGATED.AREA..1000.ha., ANNUAL.RAINFALL..Millimeters., LAND.PUT.TO.NONAGRICULTURAL.USE.AREA..1000.ha., PERMANENT.PASTURES.AREA..1000.ha. , NET.CROPPED.AREA..1000.ha. , 
```{r}
# pp_p_df = subset(pp_p_df, GROUNDNUT.AREA..1000.ha. < 400)
ground_pred = lm(pp_p_df$GROUNDNUT.AREA..1000.ha. ~ Year,data=pp_p_df)
# plot(maize_pred)

cat("\nCo-effs are ", ground_pred$coefficients, "\n")

plot(pp_p_df$Year, pp_p_df$GROUNDNUT.AREA..1000.ha.)
abline(ground_pred)
```

```{r}
pp_p_df = subset(pp_p_df, GROUNDNUT.PRODUCTION..1000.tons. < 400)
ground_pred = lm(pp_p_df$GROUNDNUT.PRODUCTION..1000.tons. ~ pp_p_df$GROUNDNUT.IRRIGATED.AREA..1000.ha. + pp_p_df$ANNUAL.RAINFALL..Millimeters. + pp_p_df$LAND.PUT.TO.NONAGRICULTURAL.USE.AREA..1000.ha. + pp_p_df$PERMANENT.PASTURES.AREA..1000.ha. + pp_p_df$NET.CROPPED.AREA..1000.ha.,data=pp_p_df)
# plot(maize_pred)

cat("\nCo-effs are ", ground_pred$coefficients, "\n")

plot(pp_p_df$GROUNDNUT.PRODUCTION..1000.tons.,pp_p_df$GROUNDNUT.IRRIGATED.AREA..1000.ha. + pp_p_df$ANNUAL.RAINFALL..Millimeters. + pp_p_df$LAND.PUT.TO.NONAGRICULTURAL.USE.AREA..1000.ha. + pp_p_df$PERMANENT.PASTURES.AREA..1000.ha. + pp_p_df$NET.CROPPED.AREA..1000.ha.)
abline(ground_pred)
```

```{r}
rice_pred = lm(pp_p_df$RICE.PRODUCTION..1000.tons. ~ pp_p_df$RICE.IRRIGATED.AREA..1000.ha. + pp_p_df$ANNUAL.RAINFALL..Millimeters. + pp_p_df$LAND.PUT.TO.NONAGRICULTURAL.USE.AREA..1000.ha. + pp_p_df$PERMANENT.PASTURES.AREA..1000.ha. + pp_p_df$NET.CROPPED.AREA..1000.ha.,data=pp_p_df)
# plot(maize_pred)

cat("\nCo-effs are ", rice_pred$coefficients, "\n")

plot(pp_p_df$RICE.PRODUCTION..1000.tons.,pp_p_df$RICE.IRRIGATED.AREA..1000.ha. + pp_p_df$ANNUAL.RAINFALL..Millimeters. + pp_p_df$LAND.PUT.TO.NONAGRICULTURAL.USE.AREA..1000.ha. + pp_p_df$PERMANENT.PASTURES.AREA..1000.ha. + pp_p_df$NET.CROPPED.AREA..1000.ha.)
abline(rice_pred)
```